---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slackteams

<!-- badges: start -->
[![Covrpage Summary](https://img.shields.io/badge/covrpage-Last_Build_2020_08_13-brightgreen.svg)](http://tinyurl.com/qq3vz59)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-win build status](https://github.com/yonicd/slackteams/workflows/R-win/badge.svg)](https://github.com/yonicd/slackteams)
[![R-mac build status](https://github.com/yonicd/slackteams/workflows/R-mac/badge.svg)](https://github.com/yonicd/slackteams)
[![R-linux build status](https://github.com/yonicd/slackteams/workflows/R-linux/badge.svg)](https://github.com/yonicd/slackteams)
[![Codecov test coverage](https://codecov.io/gh/yonicd/slackteams/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/slackteams?branch=master)
<!-- badges: end -->

`slackteams` is a part of `slackverse`

```{r,echo = FALSE, eval = TRUE}
pkgs <- sprintf('slack%s',c('calls','teams','blocks','threads','reprex'))

badges <- sprintf('%s<br>[![](https://github.com/yonicd/%s/workflows/R-mac/badge.svg)](https://github.com/yonicd/%s)',pkgs,pkgs,pkgs)

names(badges) <- pkgs

```

||||
|:-:|:-:|:-:|
||`r badges[pkgs[1]]`<br>`r emo::ji('down_left_arrow')``r emo::ji('down_arrow')``r emo::ji('down_right_arrow')`||
|`r badges[pkgs[4]]`|`r badges[pkgs[2]]`<br>`r emo::ji('left_arrow')``r emo::ji('right_arrow')`|`r badges[pkgs[3]]`<br>`r emo::ji('down_arrow')`|
|||`r badges[pkgs[5]]`|

`slackteams` is an `R` package that allows the user to manage multiple Slack teams during a session. 

## Installation

``` r
remotes::install_github("yonicd/slackteams")
```

## Tokens

Creating a token is simple using 

```r
slackteams::add_team_interactive()
```

This will generate a minimal Slack api token for you to interact with the Slack. For more information on the different permissions the token can take refer to the [Managing Tokens Vignette](articles/scopes.html)

The token team will be created, loaded and activated for you, so you can start working right away. To store this token for future sessions refer to [Storing A Token](articles/manage.html#storing-a-token).

## Basic Usage

```r
library(slackteams)
```

### Load the teams

```r
slackteams::load_teams()
# The following teams are loaded:
#   slackr, R4ds
```


### Activate a Team

```r
slackteams::activate_team('R4ds')
# slack environment variables are set to 'R4ds' supplied definitions
```

### Post a Message

```r
slackcalls::post_message(channel = validate_channel('random'),text = 'my message')
```

### Activate Another Team

```r
slackteams::activate_team('slackr')
# slack environment variables are set to 'slackr' supplied definitions
```

### Post a Message

```r
slackcalls::post_message(channel = validate_channel('random'),text = 'my other message')
```

### Editing/Deleting Posts

All messages that are posted to slack within a session are logged so you can easily edit or delete them.

#### Query posted messages

```r
slackcalls::rm_last_post()
```

#### Deleting the last message

```r
slackcalls::rm_last_post()
```
