---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slackteams

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Covrpage Summary](https://img.shields.io/badge/covrpage-Last_Build_2023_02_27-brightgreen.svg)](https://tinyurl.com/qq3vz59)
[![R-CMD-check](https://github.com/yonicd/slackteams/actions/workflows/r-cmd-check.yml/badge.svg)](https://github.com/yonicd/slackteams/actions/workflows/r-cmd-check.yml)
[![Codecov test coverage](https://codecov.io/gh/yonicd/slackteams/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/slackteams?branch=master)
<!-- badges: end -->

`slackteams` is a part of `slackverse`

```{r,echo = FALSE, eval = TRUE}
pkgs <- sprintf('slack%s',c('calls','teams','posts','blocks','threads','reprex'))

badges <- sprintf('%s<br>[![](https://github.com/yonicd/%s/actions/workflows/r-cmd-check.yml/badge.svg)](https://github.com/yonicd/%s)',pkgs,pkgs,pkgs)

names(badges) <- pkgs

```

||||
|:-:|:-:|:-:|
||`r badges[pkgs[1]]`||
|`r badges[pkgs[5]]`|`r badges[pkgs[2]]`|`r badges[pkgs[3]]`|
|||`r badges[pkgs[4]]`|
|||`r badges[pkgs[6]]`|

`slackteams` is an `R` package that allows the user to manage multiple Slack teams during a session. 

## Installation

``` r
remotes::install_github("yonicd/slackteams")
```

## Tokens

Creating a token is simple using 

```r
slackteams::add_team_interactive()
```

This will generate a minimal Slack api token for you to interact with the Slack. For more information on the different permissions the token can take refer to the [Managing Tokens Vignette](articles/scopes.html)

The token team will be created, loaded and activated for you, so you can start working right away. To store this token for future sessions refer to [Storing A Token](articles/manage.html#storing-a-token).

## Basic Usage

```r
library(slackteams)
```

### Load the teams

```r
slackteams::load_teams()
# The following teams are loaded:
#   slackr, R4ds
```


### Activate a Team

```r
slackteams::activate_team('R4ds')
# slack environment variables are set to 'R4ds' supplied definitions
```

### Query Active Team Channels

```r
slackteams::get_team_channels()
```

### Query Active Team Members

```r
slackteams::get_team_users()
```

### Activate Another Team

```r
slackteams::activate_team('slackr')
# slack environment variables are set to 'slackr' supplied definitions
```


