---
title: "Managing Tokens"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Managing Scopes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(details)
```

## Overview

`slackteams` uses incoming webhook tokens to interact with the Slack API. There are three main methods to create a token.

1. Use `slackteams::add_team_interactive` to interactively create a token for the R session.
2. Use [slackr-app](https://github.com/yonicd/slackr-app) Slack application button to create a token.
3. BYOT (Bring your own token) You are a super user or work at a company that supplied you a token. 

```{r setup}
library(slackteams)
```

### Interactive

This is similar to oauth2 implementation you would see in [googlesheets4](https://github.com/tidyverse/googlesheets4). The steps are:

1. Call the function from the `R` console
2. Authorize the creation of the token in a browser.
3. Get redirected by to the R console.

This is by far the easiest method.

The main piece that the user controls are the [permission scopes](https://api.slack.com/scopes) the token has attached to it. To help with this we use a yaml file to allow users to define locally what scopes they want to define. {slackteams} comes with its own yaml file with the scopes that are needed to use all of `slackverse`.

Click on the triangle to view the contents of the yaml. We define two "roles" in this file. 

`fields` can be 

  - `channels`:  public channels in the workspace
  - `groups`: private channels that your slack app has been added to
  - `users`: 	people in the workspace
  - `im`: direct messages that your slack app has been added to
  - `mpim`: group direct messages that your slack app has been added to
  - `emoji`: custom emoji in the workspace
  - `files`: files shared in channels and conversations that your slack app has been added to
  - `usergroups`: user groups in the workspace
  - `chat`: messages in approved channels & conversations

`actions` can be:

  - `write` access mean that you can post content in a field
  - `read` access mean that you can view basic information about a field
  - `history` access mean that you can view messages and other content in a field

The following yaml contains `base` scopes which contains only read access permissions to a token and `slackverse` specific permissions to use the packages in `slackverse`. Click the following to view the scopes of each of these settings.

```{details,details.lang = 'yml',details.summary = 'Scopes',echo= FALSE}
system.file("scopes.yml", package = "slackteams")
```

### Slackr-app

You can use the button in the main [README](https://github.com/yonicd/slackteams) page of this repository or directly at the [slackr-app](https://github.com/yonicd/slackr-app) application homepage to create the credentials identical to `slackverse` scope settings. 

### BYOT
